\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{mhchem}
\usepackage{setspace}
\usepackage{graphicx}
\setstretch{.89}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
}

\date{}
\begin{document}
\begin{center}
 \Large \sf CALDER D SHEAGREN: Curriculum Vitae\\
 { \normalsize \sf caldersheagren@gmail.com $|$ 647-700-6613 (CA) $|$ \href{https//bit.do/sheagren}{https://bit.do/sheagren}}
\end{center}

\subsection*{\sf Biographical Information}
\begin{itemize}
\item[] \textbf{Born:} Oct. 1997 in San Diego, California, USA
\item[] \textbf{Citizenship:} USA
\item[] \textbf{Languages:} English (fluent), Mandarin Chinese (learning)
\end{itemize}

\subsection*{\sf Education}

\begin{itemize}
\item[] {\bf University of Toronto}: Ph.D. Medical Biophysics. \\ 
Expected Graduation: June 2026

\item[] {\bf University of Chicago}: B.S. Mathematics with Honors,  Physics Concentration. \\ Graduated June 2020, GPA: 3.62/4.00.\\  Dean's List 2016-2017, 2017-2018, 2018-2019.

\item[]\textbf{Pacific Ridge School}: Graduated June 2016.
\end{itemize}

\subsection*{\sf Publications}
\begin{itemize}
	\item[] Gregor G. Taylor, Dmitry V. Morozov, Ciaran T. Lennon, Peter S. Barry, \textbf{Calder Sheagren}, and Robert H. Hadfield , ``Infrared single-photon sensitivity in atomic layer deposited superconducting nanowires", Applied Physics Letters 118, 191106 (2021) https://doi.org/10.1063/5.0048799

\item[] \textbf{Sheagren, C.}, Barry, P., Shirokoff, E., Tang, Q.Y., Atomic Layer Deposition Niobium Nitride Films for High-Q Resonators. \textit{J Low Temp Phys} 199, 875–882 (2020). https://doi.org/10.1007/s10909-020-02336-2

\end{itemize}

\subsection*{\sf Awards}
\begin{itemize}
	\item [] { \bf MBP Excellence Award} - SRI, Physical Sciences Platform \hfill \$6k | 2020-2021
	\item [] { \bf UChicago President's Scholarship}\hfill \$4k | 2016-2017
\end{itemize}

\subsection*{\sf Conferences Attended}
\begin{itemize}
\item[] {\bf Canarie Research Software Conference} 2021 (Virtual | Lightning Talk).
\item[] {\bf UToronto MBP Department Symposium} 2021 (Toronto, ON | Poster).
\item[] {\bf Low Temperature Detectors} Workshop 2019 (Milan, Italy | Poster).
\item[] {\bf American Physical Society} 2019 March Meeting (Boston, MA. | Talk). 
\item[] {\bf American Vacuum Society} 2018 Prairie Chapter Symposium (Chicago, IL | Poster). 
\end{itemize}

\subsection*{\sf Research \& Internships}
\begin{itemize}
  \item[] \textbf{UToronto: Cardiac MRI}: Cardiac Magnetic Resonance Imaging and Topological Data Analysis for Arrhythmia Substrate Characterization. \emph{Ph.D. Research Project.} August 2020 - Present.  \hfill {\href{https://medbio.utoronto.ca/faculty/wright}{(Graham$\,\,$Wright)}}
\item[] \textbf{UChicago: MKIDs}: Fabricating novel Atomic Layer Deposition nitrides for resonator-based CMB detectors. November 2017 - June 2020. \hfill (\href{http://kicp.uchicago.edu/~shiro/erik/}{Erik$\,\,$Shirokoff})
\item[] \textbf{UChicago: X-Ray Optics}: Simulating nanofabricated collimator for 100nm-resolution X-ray tomography at APS beamline. September 2019 - June 2020. \hfill (\href{https://voices.uchicago.edu/larivierelab/}{Patrick$\,\,$La$\,$Rivi\`ere})
\item[] \textbf{Fermilab: Accelerator Materials}: Electron irradiation and superconducting niobium and niobium-tin. -- Summer 2019 Lee Teng Internship.  \hfill (\href{https://www.linkedin.com/in/tiziana-spina-74114646}{Tiziana$\,\,$Spina})


\end{itemize}

\subsection*{\sf Teaching Experience}
\begin{itemize}
\item[] \textbf{UChicago:}
\item[] MATH 131-132 (Introductory Calculus): Junior Tutor Aut 2017 \& Win 2020
\item[] MATH 151-153 (Calculus): Course Assistant Win/Spr/Aut 2018, Win/Spr 2019
\item[] MATH 195-196 (Multivariable Calculus and Linear Algebra): Spr 2018 \& Win 2020
\item[] MATH Dept. General Tutor: Spr 2020

\end{itemize}

\subsection*{\sf Outreach}
\begin{itemize}
  \item[] {\bf UToronto Fac. Medicine Saturday Program}: Tutor, Nov. 2020 - Apr. 2021.
\item[] {\bf SRI Student Network}: Contributing member, Sep. 2020 - Sep. 2021.
\item[] {\bf UChicago Math REU}: Mentor, June 2020-Sep. 2020. Papers mentored: [\href{https://math.uchicago.edu/~may/REU2020/REUPapers/Chen,Andrew.pdf}{1}, \href{https://math.uchicago.edu/~may/REU2020/REUPapers/Ghorbani.pdf}{2}, \href{https://math.uchicago.edu/~may/REU2020/REUPapers/Zhuang,Yuerong.pdf}{3}]
\item[] {\bf UChicago Math Club}: President, Sep. 2019-June 2020.\\
\end{itemize}

 \subsection*{\sf Open-Source Software Development}

\begin{itemize}

        \item[] {\bf Scikit-TDA}: Collaborator on effort to include persistence landscapes in open-source python topology analysis software. Jan. 2021 - Feb. 2021.

  \item[] {\bf Rocky Linux Foundation}: Documentation Team member, quality assurance and administration support. Dec. 2020 - Present.

\end{itemize}

\subsection*{\sf Computation Skills}

\begin{itemize}
\item[] \textbf{Competent}: Python, \LaTeX, vim, markdown
\item[] \textbf{Proficient}: bash, git, HTML, emacs, reveal.js
\end{itemize}

\subsection*{\sf Other Interests}
\begin{multicols}{2}
\begin{itemize}
\item[] Nanofabrication
\item[] Machine shop \& soldering
\item[] Photography (\href{https://www.flickr.com/photos/155448890@N05/}{Flickr})
\item[] Second degree black belt
\item[] Music: piano, saxophone, clarinet
\item[] Action/Spy/Superhero movies
\end{itemize}
\end{multicols}

\vfill
\flushright (Updated July 2021)
\end{document}
